---
title: "HDBSCAN London"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HDBSCAN London}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  eval= TRUE, # change to TRUE to produce the vignette and FALSE for the package build
  comment = "#>"
)
```

```{r setup, echo=FALSE, message=FALSE}
library(leaflet)
library(htmltools)
library(sp)
library(dplyr)
library(htmlwidgets)
# library(gambling.neighbourhoods)
library(devtools)
load_all()
```

This vignette demonstrates how to create interactive maps using the `leaflet` package in R to visualize the gambling neighbourhoods identified using an hybrid approach combining HDBSCAN clustering with a fixed eps=500m specifically for London.
Check the main vignette [HDBSCAN_eps500](HDBSCAN_eps500.html) for general details about the methodology and the approach used.


📝 **Note:** Results for MinPts=2 and 3 are not shown here as they produced a very high number of clusters (over 100) which are difficult to visualise and interpret on a map.

<br>

## Load data
Load the geographical data (spatial points dataframe) containing the coordinates of gambling premises in London.  
```{r load-data, echo=TRUE, message=FALSE}
xy_london <- readRDS("data/xy_london.rds")
``` 


## MinPts=4 
```{r k4_eps500, message=FALSE}
res4_eps500 <- readRDS("results/hdbscan_results_eps500_MinPts4_london.rds")
# Create a data frame from the spatial points   
df4_eps500 <- create_df(res4_eps500,xy_london)
head(df4_eps500)
dim(df4_eps500)
```
Number of clusters (excluding noise):
```{r num-clusters-k4-eps500, message=FALSE}
k4_eps500 <- length(unique(df4_eps500$cluster)) - 1
k4_eps500
```
Number of noise points:
```{r num-noise-k4-eps500, message=FALSE}
df4_eps500_null <- create_df_null(df4_eps500)
n_noise_k4_eps500 <- nrow(df4_eps500_null)
n_noise_k4_eps500
```
Leaflet map 
```{r leaflet-map-k4, message=FALSE}
# Get the convex hulls for each cluster
cluster_hulls4 <- get_cluster_hulls(df4_eps500)
# Create the leaflet map
map_k4_eps500 <-leaflet_map(cluster_hulls4, df4_eps500, df4_eps500_null)
# saveWidget(map_k4_eps500, file="results/map_MinPt4_eps500.html")
map_k4_eps500
```
## MinPts=5 
```{r k5_eps500, message=FALSE}
res5_eps500 <- readRDS("results/hdbscan_results_eps500_MinPts5_london.rds")
# Create a data frame from the spatial points
df5_eps500 <- create_df(res5_eps500,xy_london)
head(df5_eps500)
dim(df5_eps500)
```
Number of clusters (excluding noise):
```{r num-clusters-k5-eps500, message=FALSE}
k5_eps500 <- length(unique(df5_eps500$cluster)) - 1
k5_eps500
```
Number of noise points:
```{r num-noise-k5-eps500, message=FALSE}
df5_eps500_null <- create_df_null(df5_eps500)
n_noise_k5_eps500 <- nrow(df5_eps500_null)
n_noise_k5_eps500
```
Leaflet map
```{r leaflet-map-k5, message=FALSE}
# Get the convex hulls for each cluster
cluster_hulls5 <- get_cluster_hulls(df5_eps500)
# Create the leaflet map
map_k5_eps500 <-leaflet_map(cluster_hulls5, df5_eps500, df5_eps500_null)
# saveWidget(map_k5_eps500, file="results/map_MinPt5_eps500.html")
map_k5_eps500
```

## Summary statistics
Summary table with number of clusters and noise points for each MinPts value.

```{r summary-table, message=FALSE}
summary_table <- data.frame(
  MinPts = c(4, 5),
  Num_Clusters = c(k4_eps500, k5_eps500),
  Num_Noise_Points = c(n_noise_k4_eps500, n_noise_k5_eps500)
)
summary_table
```

